---
title: "Lista de Exercícios"
author: "Samuel Macêdo"
date: "5 de março de 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

```{r bibliotecas}
library(knitr)
source("gerar_sequencia.R", encoding = "UTF-8")
source("Estatistica_descritiva.R",encoding = "UTF-8")
```

```{r gerar_sequencias}
assime <- c(-1.5, -0.8, -0.2, 0.2, 0.8, 1.5)
curto <- c(0.15, 0.2, 0.26, 0.26, 0.3, 0.35)

parametros <- data.frame(qtd_num = sample(25:40, 10, replace = TRUE),
                         assimetria = sample(assime, 10, replace = TRUE), 
                         curtose = sample(curto, 10, replace = TRUE),
                         inicio = sample(1:20, 10, replace = TRUE)
                         )
result <- list()
for( i in 1:10){
  
  result[[i]] <- gerar_sequencia(qtd_num = parametros$qtd_num[i],
                                 target_assimetria = parametros$assimetria[i],
                                 target_curtose = parametros$curtose[i],
                                 inicio = parametros$inicio[i])
  
}

```

# Calcule assimetria e curtose. Classifique.

### 1) `r sort(result[[1]]$sequencia)`
       `r kable(result[[1]]$estatisticas_descritivas)`
       
### 2) `r sort(result[[2]]$sequencia)`
       `r kable(result[[2]]$estatisticas_descritivas)`

\newpage       
### 3) `r sort(result[[3]]$sequencia)`
       `r kable(result[[3]]$estatisticas_descritivas)`
       
### 4) `r sort(result[[4]]$sequencia)`
       `r kable(result[[4]]$estatisticas_descritivas)`

\newpage 
### 5) `r sort(result[[5]]$sequencia)`
       `r kable(result[[5]]$estatisticas_descritivas)`

### 6) `r sort(result[[6]]$sequencia)`
       `r kable(result[[6]]$estatisticas_descritivas)`

\newpage        
### 7) `r sort(result[[7]]$sequencia)`
       `r kable(result[[7]]$estatisticas_descritivas)`
       
### 8) `r sort(result[[8]]$sequencia)`
       `r kable(result[[8]]$estatisticas_descritivas)`

\newpage 
### 9) `r sort(result[[9]]$sequencia)`
       `r kable(result[[9]]$estatisticas_descritivas)`
       
### 10) `r sort(result[[10]]$sequencia)`
        `r kable(result[[10]]$estatisticas_descritivas)`
       


